The Right Way to Search Evolving Graphs

### 2016-03-04 paper.tex
add new experiments and update comments

We generate a group of random (directed) \texttt{IntEvolvingGraph}s
with $8,000$ active nodes and $4$ time stamps.
At each time stamp $i$, a static edge is included in $G^{[i]} \in G_4$ with
probability $p$. Note that in this experiment, we do not have direct control
over the full edge set $E$, only the static edge set $\tilde E$. However, the
causal edge set $E'$ can grow at most by $O(\tilde E)$, so it suffices to demonstrate
linear scaling in $|\tilde E|$.
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a Linux system with Intel(R) Core(TM) i7-3537U CPU @ $2.00$GHz.

The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with the result of Theorem \ref{thm:complexity}.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.44]{time.pdf}
  \caption{Experimental run time and memory use of Algorithm \ref{alg:bfs}
on a collection of random evolving graphs with $8,000$ active nodes and $4$ time
stamps, showing linear scaling in $|\tilde E|$. The horizontal axis shows the
number of edges ($|\tilde E|$, including both static and causal edges) of each evolving
graph, while the vertical axis shows the corresponding
computation time.}
  \label{fig:time}
\end{figure}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.

>>>>

We generate a group of random (directed) \texttt{IntEvolvingGraph}s
with $1.0\times 10^5$ active nodes and $10$ time stamps.
The first random \texttt{IntEvolvingGraph} in the group has 
$1.0 \times 10^8$ static edges.
We consecutively add $5.0\times 10^7$
random static edges to this \texttt{IntEvolvingGraph}. For example, 
the second random \texttt{IntEvolvingGraph} in the group has about $1.5 \times 10^8$ static edges and the third
has about $2.0 \times 10^8$ static edges.
% At each time stamp $i$, a static edge is included in $G^{[i]} \in G_4$ with
% probability $p$. 
Note that in this experiment, we do not have direct control
over the full edge set $E$, only the static edge set $\tilde E$. However, the
causal edge set $E'$ can grow at most by $O(\tilde E)$, so it suffices to demonstrate
linear scaling in $|\tilde E|$. 
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a Linux system with Intel(R) Xeon(R) CPU E7-8850 @ $2.00$GHz.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with the result of Theorem \ref{thm:complexity}.
By doing this experiment, we find that it takes longer and longer time to 
add new static edges, since we also need to include
all the causal edges introduced by these new static edges.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.58]{time.pdf}
  \caption{Experimental run time and memory use of Algorithm \ref{alg:bfs}
on a collection of random evolving graphs with $1.0\times 10^5$ active nodes and $10$ time
stamps, showing linear scaling in $|\tilde E|$. The horizontal axis shows the
number of edges ($|\tilde E|$, including only the causal edges) of each evolving
graph, while the vertical axis shows the corresponding
computation time.}
  \label{fig:time}
\end{figure}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.
